Through the eyes of the teacher

### 2022-03-01 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
r markdown method part

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Egelstraße 2a 04103 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Dr. Gregor Kachel"
    affiliation   : "1, 2"
  - name          : "Dr. Christin Lotz"
    affiliation   : "1"
  - name          : "Prof. Dr. Anne Deiglmayr"
    affiliation   : "1"

@@

authornote: |
  The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project. The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.

abstract: |
  This document is a supplement to the paper and shows first graphs findings from the pilot study.

keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
wordcount         : "1949"

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Male" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

>>>>

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Dittrichring 5-7, 04109 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Dr. Gregor Kachel"
    affiliation   : "1, 2"
  - name          : "Dr. Christin Lotz"
    affiliation   : "1"
  - name          : "Prof. Dr. Anne Deiglmayr"
    affiliation   : "1"

@@

authornote: |
  Ethics Approval 
All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board. The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.

  Consent to Participate
All participants gave informed consent.

abstract: |

keywords          : "Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking"
wordcount         : "XXX"

@@

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender male" = round(100 * n() / nrow(Gende)), 2,
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

### 2022-03-01 02_paper/01_pilot/paper_1/plots_peer/GRI_Graphics_Notebook_Peer.Rmd
r markdown method part

ggplot(data = df_gri_comp,
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

>>>>

ggplot(data = filter(df_gri_comp,
                     TOI != "Calibration phase"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

### 2022-03-01 02_paper/01_pilot/paper_1/plots_peer/presentation_plots.Rmd
r markdown method part

```{r include=FALSE,warning=FALSE,message=FALSE}
library(needs)
needs(tidyverse,
      gridExtra,
      viridis,
      ggthemes)

@@

>>>>

```{r include=FALSE,warning=FALSE,message=FALSE}
library(needs)
needs(tidyverse,
      gridExtra,
      viridis,
      ggthemes,
      RColorBrewer)

@@

## Mean Duration

```{r}
group_by(.data = df_gri,
         TOI) %>% summarise(`Mean Duration Fix`= mean(`M Dur Fix`)) %>%
  ggplot(mapping = aes(x = TOI,
                     y = `Mean Duration Fix`
                     )
         ) +
  geom_bar(stat = "identity",
           color = "black",
           fill = "#EF8A62") +
  theme_clean() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1
                                   )
        )
```

### 2022-03-01 02_paper/01_pilot/paper_1_supplement.Rmd
r markdown method part

@@

# create a basic table (tibble) using tidyverse functions 
scale.quest.table <- quest.raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2))

@@

quest.plot <- quest.raw.data %>%
  ggplot( aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot

>>>>

# knock out NAs and filter only perspective == teacher, student
quest.raw.data <- quest.raw.data  %>% filter(
  personID != "NA",
  str_detect(perspective, paste(c("teacher", "student"),collapse = '|')))

@@

# create a basic table (tibble) using tidyverse functions 
scale.quest.table <- quest.raw.data %>% # select data
  group_by(scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "SD scale" = round(sd(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value))

@@

quest.plot <- quest.raw.data %>%
  ggplot(aes(x=scale, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~group)+
    ggtitle("Boxplot with individual points for all scales") +
    xlab("")
quest.plot
